\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2024-03-19 TilingProjectDraft/tilingProject.tex
updated real space Greens function section

The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{cluster-bath.pdf}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure*}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.

@@

\begin{figure}[!htb]
 	\centering
 	\includegraphics[width=0.48\textwidth]{gen_siam.pdf}
 	\caption{Cluster+bath construction of auxiliary model. It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the cluster and the zeroth site have onsite correlations.}
 \end{figure}
 The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice. Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
 \begin{equation}\begin{aligned}
	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
 \end{aligned}\end{equation}
where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster. To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons. The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.

@@

\subsection{Formal description of the tiling procedure}
We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian. The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model. The local behaviour of this impurity model should reflect the essential local physics of the lattice model. Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction. We will henceforth refer to this site as the zeroth site. In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout. In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\). The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
\end{aligned}\end{equation}
where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.

In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice. For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\). In terms of manybody states and operators, their action is defined as 
\begin{equation}\begin{aligned}\label{translationDefinition}
	T^\dagger({\bf a}) \ket{\bf r_1, \bf r_2,\ldots} &= \ket{\bf r_1 + a, \bf r_2 + a,\ldots}\\
	T^\dagger({\bf a}) \mathcal{O}\left(\bf r_1, \bf r_2,\ldots\right)T({\bf a}) &= \mathcal{O}\left(\bf r_1 + a, \bf r_2 + a,\ldots\right)~,
\end{aligned}\end{equation}
where \(\)
For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have 
\begin{equation}\begin{aligned}
	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})
\end{aligned}\end{equation}
It acts similarly on the auxiliary model Hamiltonian:
\begin{equation}\begin{aligned}
	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
\end{aligned}\end{equation}
translating all sites by the vector \({\bf a}\). The auxiliary model, being an impurity model, lacks translation symmetry. The lattice model does remain invariant under global translation operations. In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
\begin{equation}\begin{aligned}
	\label{tilingPrescription}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
\end{aligned}\end{equation}
where \({\bf r}\) sums over all lattice sites.

\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath. The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\). Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes. We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model). The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
\end{aligned}\end{equation}
where \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath. Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath. We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)). We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength. Note that the impurity site and the conduction bath are both at half-filling.

@@

The result of the tiling operations is a Hubbard-Heisenberg model, of the form
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 \\
						  &- \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}~,
\end{aligned}\end{equation}
where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model). By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
\begin{equation}\begin{aligned}
	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
\end{aligned}\end{equation}
In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}~,
\end{aligned}\end{equation}
using which the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.

@@

\section{Form of the eigenstates: Bloch's theorem}
In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}({\bf r})} = \sum_{{\bf r}_i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i({\bf r} - {\bf r}_i)}\). Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T({\bf a})\) by some lattice distance \({\bf a}\):
\begin{equation}\begin{aligned}
	T({\bf a})\ket{\Psi_{{\bf k}}\left({\bf r}\right)} = \ket{\Psi_{{\bf k}}({\bf r} + {\bf a})} = e^{-i{\bf k}\cdot{\bf a}}\ket{\Psi({\bf r})}
\end{aligned}\end{equation}
These translation operators share eigenstates with the crystal momentum operator:
\begin{equation}\begin{aligned}
	T\left( {\bf r} \right) \ket{{\bf k}} = e^{-i {\bf k}\cdot{\bf r}} \ket{{\bf k}}~.
\end{aligned}\end{equation}
As a result, the eigenstates can be labelled using the crystal momentum value \({\bf k}\), along with a band index \(n\). The eigenstates \(\ket{\Psi_{{\bf k},n}}\) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}). This means that the eigenstates \(\psi_n\left({\bf r}_d\right)\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian. The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.

The state \(\psi_n\left({\bf r}_d\right)\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself is an averaged Hamiltonian over \(\mathcal{Z}\) zeroth sites. Accordingly, we can express the averaged eigenstate \(\psi_n\left({\bf r}_d\right)\) as
\begin{equation}\begin{aligned}
	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
\end{aligned}\end{equation}
where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\). With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi_{{\bf k}, n}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}, {\bf a}\right)}
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \({\bf k}\) and \(n\) to 0:
\begin{equation}\begin{aligned}
	\ket{\Psi_\text{gs}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}, {\bf a}\right)}
\end{aligned}\end{equation}

>>>>

The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.48\textwidth]{clusterBath.pdf}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.

@@

\begin{figure}[!htb]
 	\centering
 	\includegraphics[width=0.4\textwidth]{gen_siam.pdf}
 	\caption{Cluster+bath construction of auxiliary model. It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the cluster and the zeroth site have onsite correlations.}
 \end{figure}
 The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice. Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
 \begin{equation}\begin{aligned}
	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
 \end{aligned}\end{equation}
where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster. To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons. The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.

@@

\subsection{Formal description of the tiling procedure}\label{formalDescription}
We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian. The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model. The local behaviour of this impurity model should reflect the essential local physics of the lattice model. Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction. We will henceforth refer to this site as the zeroth site. In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout. In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\). The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
\end{aligned}\end{equation}
where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.

In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice. For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\). In terms of manybody states and operators, their action is defined as 
\begin{equation}\begin{aligned}\label{translationDefinition}
	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
\end{aligned}\end{equation}
where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions. For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have 
\begin{equation}\begin{aligned}
	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
\end{aligned}\end{equation}
It acts similarly on the auxiliary model Hamiltonian:
\begin{equation}\begin{aligned}
	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
\end{aligned}\end{equation}
translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
\begin{equation}\begin{aligned}
	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
\end{aligned}\end{equation}
it is easy to see that the total momentum states are eigenstates of the global translation operators:
\begin{equation}\begin{aligned}
	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
\end{aligned}\end{equation}
where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.

The auxiliary model, being an impurity model, lacks translation symmetry. The lattice model does remain invariant under global translation operations. In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
\begin{equation}\begin{aligned}
	\label{tilingPrescription}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
\end{aligned}\end{equation}
where \({\bf r}\) sums over all lattice sites.

\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath. The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\). Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes. We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model). The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
\end{aligned}\end{equation}
where 
\begin{itemize}
	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
\end{itemize}
Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath. We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)). We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength. Note that the impurity site and the conduction bath are both at half-filling.

@@

The result of the tiling operations is a Hubbard-Heisenberg model, of the form
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
\end{aligned}\end{equation}
where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model). By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
\begin{equation}\begin{aligned}
	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
\end{aligned}\end{equation}
In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}~,
\end{aligned}\end{equation}
using which the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.

@@

\section{Form of the eigenstates: Bloch's theorem}
In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians. Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
\begin{equation}\begin{aligned}
	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
\end{aligned}\end{equation}
The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}. It was shown there that they share eigenstates with the total momentum operator. In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process. As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).

The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}). This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian. The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.

The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites. Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
\begin{equation}\begin{aligned}
	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
\end{aligned}\end{equation}
where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\). With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}\label{eigenstateProposal}
	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
				&= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings. The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands. The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
\begin{equation}\begin{aligned}
	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} \\
			     &= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
\end{aligned}\end{equation}
